\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mathabx}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
 
\newenvironment{list1}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\circ$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\begin{document}

\name{\LARGE Satabdi Das} \hfill {\em \today}

\begin{resume}
\section{\sc Contact Information}

\vspace{.05in}
Phone:  (+1) 9789547916\\
E-mail:  satabdidas@gmail.com\\
Website: \url{majantali.net}


%\section{\sc Summary}
%\begin{list2} %Summary%
%\item Have more than years of experience in C/C++ developing large and complex software systems on the Linux platform used by companies in the Semiconductor industry.
%\item Have expertise in object oriented design, implementing them and building optimal data structures. 
%\item Have worked independently on projects to deliver high quality outcome.
%\item Open source enthusiast. Developed an open source GeoIP library from scratch which is now a part of GeoClue project.\\
%\end{list2}

%%%%%%%%%%%%%%%%%%%
\section{\sc Professional Experience}
%%%%%%
{\bf   Mentor Graphics}
\hfill {\bf Member of Consulting Staff}
\hfill{\bf December 2016 -- Present}
\vspace{.05in}
\begin{list1} %Job Description%
	\item Veloce Emulator Platform
	\begin{list2}
		\item Improved the run time performance of the scheduler ranging from 10\%-30\%.
		\item Designed and developed critical features and redesigned the core algorithm of the critical path finder tool.
		\item Improved unit test coverage and started introducing modern C++ code.
		\item Organized lunch and learn sessions on topics in modern C++.	
	\end{list2}
\end{list1}
%%%%%%

{\bf   Mentor Graphics}
\hfill {\bf Member of Consulting Staff}
\hfill{\bf April 2013 -- July 2016}
\vspace{.05in}
\begin{list1} %Job Description%
	\item Veloce Prototyping System
	\begin{list2}
		\item Designed and developed the logging system.
		\item Implemented robust object oriented components.
		\item Organized tech-talks to share and enhance technical knowledge and promote best programming practices and was a member of all-India technical council in the company.
	\end{list2}
	\item Questa Static
	\begin{list2}
		\item Developed new components and improved the existing features.
		\item Improved the run-time performance by as much as 6x in critical customer issues.
		\item Re-factored and improved quality of the code which in turn gave performance gain in memory.
	\end{list2}
\end{list1}
%%%%%%
{\bf   Gnome Foundation}
\hfill {\bf Programming Intern}
\hfill{\bf January 2013 -- April 2013}
\vspace{.05in}
\begin{list1} %Job Description%
\item Designed and developed GeoIP and WiFi based geo-location server and client libraries for Gnome from scratch. This library later became part of GeoClue which provides location information. The source code is at \url {http://git.gnome.org/browse/geocode-glib}
\end{list1}
%%%%%%%
{\bf   Mirafra Technologies}
\hfill {\bf Senior Software Engineer}
\hfill{\bf October 2008 -- January 2010}
\vspace{.05in}
\begin{list1} %Job Description%
\item Developed various components in the parser and elaborator of a fast spice simulator.
\item Automated the regression set up of the product Cooolgate from Pwrlite Inc.
\end{list1}
%%%%%%%%%
{\bf   Interra Systems}
\hfill {\bf Senior Member of Technical Staff}
\hfill{\bf June 2006 -- September 2008}
\vspace{.05in}
\begin{list1} %Job Description%
\item Improved syntactic and semantic checking of an object-oriented parser and analyzer. Worked on performance improvement of the analyzer.
\item Developed a part of an efficient object-oriented data converter called area-generator.
\end{list1}
%%%%%%%%%
{\bf   Wipro Technologies}
\hfill {\bf Software Engineer}
\hfill{\bf August 2005 -- May 2006}
\vspace{.05in}
\begin{list1} %Job Description%
\item Developed a web application using JAVA/J2EE, Struts framework.\\
\end{list1}

%\vspace{.5in}
\section{\sc Technical Skills}
C, C++ using object-oriented programming concepts\\
Operational knowledge of Perl, Python, Go and Shell scripting\\

\section{\sc Education}
{\bf Recurse Center, New York} \hfill {\bf August 2016 -- November 2016}\\
%\vspace*{-.1in}
Explored low level systems programming and distributed systems during the batch.\\
{\bf Jadavpur University, India} \hfill {\bf 2005}\\
%\vspace*{-.1in}
B.E in Computer Science and Engineering \hfill(77\%, First Class with Honours)\\

\section{\sc Achievements}
\begin{list2} %Achievements%
\item Selected in the Gnome-led Outreach Program for Women in 2013 \url {https://wiki.gnome.org/OutreachProgramForWomen/2013/JanuaryApril/Accomplishments}
\item Awarded Interra Team Performance Award-2007 for significant contribution to the project in Interra Systems\\
\end{list2}
\section{\sc Projects}
\begin{list2} %Projects%
\item Developed an object-oriented preprocessor used in combinatorial auction, an e-commerce application project under the guidance of Merlin Nandy, doctoral candidate, Management Information Systems, IIM Calcutta, and supervised by Prof. Ambuj Mohanti, Management Information Systems, IIM Calcutta.
\item Worked on “Voice over Local Area Network (LAN)” project under the guidance of Prof. Atal Chaudhuri, Jadavpur University.
\end{list2}
\section{\sc Interests}
\begin{list2} %Interests%
\item Co-founded Boston Hack \&\& Tell meetup for programmers.
\item Co-organized resume camp and career camp for women in the software industry in India.
\item Co-organized C++11 meetups in Delhi NCR.
\item Tinkers with wearable electronics and Arduino.
\end{list2}

\end{resume}
\end{document}




